---
title: "Deprecated Code Investigation"
output: html_notebook
---

###  Write out the JSON 

Here I want to alter the punctuation of the JSON file so that I can experiment with the data.  My theory is that the SAD system is generating mal-formed JSON and that adding square brackets to the record will make it easier to manipulate

```{r}
write_json(sad_person, "sadp.json")
```


Then used Notepad++ to add `[` and `]` to the begining and end, respectively.  (Could have done this inside the RStudio editor.)  Now I want to read in this modified JSON file.

```{r}
sadp_with_bracket <- read_json("sadp_with_bracket.json",
                               simplifyVector = TRUE)

foo <- read_json("sadp.json")

write_json(got_chars, "sw_chars.json")

foo <- read_json("sw_chars.json")
```

### Resulting Discovered Problems

I can write https://jsonformatter.curiousconcept.com/and subsequently read in the sw_chars.json  but I get errors when I try to do the same with the Scholars At Duke json data.  So now I'm going to try some JSON validators

- https://jsonlint.com/
- https://jsonformatter.curiousconcept.com/


Both tools report that the **JSON format is valid**.  So that shoots that theory.

### Wait Wait Wait

I took a closer look at the validated JSON and it looks like the validator did change the JSON punctuation formatting.  Let me try and read that in...

```{r}
valid_json <- read_json("delinted_validated_data.json")
```


Yeah, that seemed to make a difference.  Notice the difference in reported data structures

sad_person is a `r class(sad_person)`


```{r}
class(got_chars)
class(sad_person)
class(valid_json)
```

Although `class()` reports all three as lists, the Environment tab reports *sad_person* (read in via URL -- `fromJSON`) as a "List of 24".  Whereas, `class()` reports *valid_json* (read in via `read_json`) as a "Large list (24 elements, 578.6 Kb)"

Let's check what would happen if we read in the *repurrrsive::got_char* onboard JSON data....

```{r}
foo_sw_chars <- read_json("sw_chars.json")
```


```{r}
View(foo_sw_chars)
View(valid_json)
```

O.K.  It seems to make no difference

## Simplify

Now I'm going to look into what happens if I just take the first 5 "rows" of the JSON file.


```{r}
super_small <- read_json("super_small.json")
```



## Flatten Test

```{r}
map(got_chars, "id") %>% 
  flatten_int()
```

```{r}

View(got_chars)
map(got_chars, "id") %>% 
  flatten_chr()
  #flatten_int()
```


```{r}
map(got_chars, "titles") %>% 
  flatten("titles")
```

```{r}
flatten(got_chars)
```

```{r}
map(got_chars, "titles") %>% 
  flatten_chr()
```


```{r}
sad_person$positions %>% 
  jsonlite::flatten()
```

