---
title: "list to dataframe"
author:  "John Little"
output: html_notebook
---


The following is HTML output for the R Notebook, list_to_dataframe.Rmd and illustrates how to take a list column in a dataframe and wrangle it, thus making it easier to analyze

From a Jenny Bryan Workshop but similar to [Purrr tutorial](https://jennybc.github.io/purrr-tutorial/):  [Food Markets in New York](https://jennybc.github.io/purrr-tutorial/ex26_ny-food-market-json.html) 

## Load Packages

- purrr  -- a package for iterating over lists
- repurrrsive -- a package for learning purrr

```{r}
library(purrr)
library(repurrrsive)

## The following are helpful tidyverse packages.  
library(tibble)
library(dplyr)
library(tidyr)
```

Could have more simply loaded tidyverse & repurrrsive packages, but we're learning here.

```{}
library(tidyverse)
library(repurrrsive)
```


## Assign onboard list *got_chrs* to an list *sw_characters*

```{r}
sw_characters <- got_chars
```

## Simplify the list

select list items (*name*, and *titles*) to work on, transform them to a data frame with two variables.  One variable is a character vector, the other variable is a list -- because a single named character can have many alegiances (i.e. titles).

```{r}
dataframe_list <- tibble(
  name = map_chr(sw_characters, "name"),
  title = map(sw_characters, "titles")
)

dataframe_list
```

## Transform 
from nested list, to "unfilled" tall, then filldown (i.e. `unnest()`)

```{r}
dataframe_list %>% 
  mutate(n_titles = map_int(title, length)) %>% 
  filter(n_titles > 1) %>% 
  select(name, title) %>% 
  unnest()
```


