---
title: "More Futzing with JSON lists"
output: html_notebook
---

## Load Packages
```{r}
library(tidyverse)
library(jsonlite)
library(repurrrsive)
```

## Load Data

https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri=https://scholars.duke.edu/individual/per5862252

```{r}
sad_person <- fromJSON("https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri=https://scholars.duke.edu/individual/per5862252")
```

###  Write out the JSON 

Here I want to alter the punctuation of the JSON file so that I can experiment with the data.  My theory is that the SAD system is generating mal-formed JSON and that adding square brackets to the record will make it easier to manipulate

```{r}
write_json(sad_person, "sadp.json")
```


Then used Notepad++ to add `[` and `]` to the begining and end, respectively.  (Could have done this inside the RStudio editor.)  Now I want to read in this modified JSON file.

```{r}
sadp_with_bracket <- read_json("sadp_with_bracket.json",
                               simplifyVector = TRUE)

foo <- read_json("sadp.json")

write_json(got_chars, "sw_chars.json")

foo <- read_json("sw_chars.json")
```

### Resulting Discovered Problems

I can write https://jsonformatter.curiousconcept.com/and subsequently read in the sw_chars.json  but I get errors when I try to do the same with the Scholars At Duke json data.  So now I'm going to try some JSON validators

- https://jsonlint.com/
- https://jsonformatter.curiousconcept.com/


Both tools report that the **JSON format is valid**.  So that shoots that theory.

### Wait Wait Wait

I took a closer look at the validated JSON and it looks like the validator did change the JSON punctuation formatting.  Let me try and read that in...

```{r}
valid_json <- read_json("delinted_validated_data.json")
```


Yeah, that seemed to make a difference.  Notice the difference in reported data structures

sad_person is a `r class(sad_person)`


```{r}
class(got_chars)
class(sad_person)
class(valid_json)
```

Although `class()` reports all three as lists, the Environment tab reports *sad_person* (read in via URL -- `fromJSON`) as a "List of 24".  Whereas, `class()` reports *valid_json* (read in via `read_json`) as a "Large list (24 elements, 578.6 Kb)"

Let's check what would happen if we read in the *repurrrsive::got_char* onboard JSON data....

```{r}
foo_sw_chars <- read_json("sw_chars.json")
```


```{r}
View(foo_sw_chars)
View(valid_json)
```

O.K.  It seems to make no difference

## Simplify

Now I'm going to look into what happens if I just take the first 5 "rows" of the JSON file.


```{r}
super_small <- read_json("super_small.json")
```



## Flatten Test

```{r}
map(got_chars, "id") %>% 
  flatten_int()
```

```{r}

View(got_chars)
map(got_chars, "id") %>% 
  flatten_chr()
  #flatten_int()
```


```{r}
map(got_chars, "titles") %>% 
  flatten("titles")
```

```{r}
flatten(got_chars)
```

```{r}
map(got_chars, "titles") %>% 
  flatten_chr()
```


```{r}
sad_person$positions %>% 
  jsonlite::flatten()
```


## Pick Up Here

```{r}
sad_person$positions %>% 
  purrr::flatten()

sad_person %>% 
  purrr::flatten()

#jsonlite::flatten(super_small)
```

```{r}
names(sad_person[[8]])
names(sad_person[[6]])
```

```{r}
sad_person[[6]]
```

```{r}
sad_person[["title"]]
sad_person[["label"]] 
sad_person[["publications"]]
```


```{r}
purrr::flatten(sad_person)
map(sad_person, "uri")
```


```{r}
map(sad_person, "label")
```


```{r}
sad_person[[4]]
```


```{r}
map_chr(sad_person[["label"]], 1)
map_chr(sad_person[["title"]], 1)
sad_person[["title"]]
map_chr(sad_person[["vivoType"]], 1)
map_chr(sad_person[["uri"]], 1)
#map(sad_person, 6)
sad_person[["publications"]] 
sad_person[["awards"]] 
sad_person[["awards"]][["attributes"]]

#(award_labels <- map_chr(sad_person[["awards"]]$label, 1))
as.list(sad_person$awards$label)

```


```{}
## list-columns = lists in a data frame ----
gt <- tibble(
  name = map_chr(got_chars, "name"),
  houses = map(got_chars, "allegiances")
)
View(gt)
```




```{r}
person_awards_df <- tibble(
  name = sad_person$label,
  title = sad_person$title,
  #awards = as.list(sad_person$awards$label)
  #awards = map(sad_person$awards$label, 1)
  awards = sad_person$awards$label
)

#person_awards_df$awards[3]
person_awards_df
```



```{r}
map(sad_person$awards, 2)

sad_person$awards$label
```

