---
title: "Testing our Idea"
output: html_notebook
---

## Load Packages

```{r}
library(jsonlite)
library(tidyverse)
library(glue)
```

## Get Scholars @ Directory information


```{r}
org_rec <- "https://scholars.duke.edu/widgets/api/v0.9/organizations/people/all.json?uri=https://scholars.duke.edu/individual/org50000498&formatting=detailed&style=yes&start=&end="
```


```{r}
org_links <- fromJSON(URLencode(org_rec))

org_links
```


## Logic Outline

Using either a for loop or map, loop over each row of the org_links data frame, take the uri field and gather more information.

more_info <- org_links$uri

## Example

**The following contains no Logic loops (either "for", or "map")**

### build a URL:

```{r}
baseurl <- "https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri="

person_link <- glue(baseurl, org_links$uri[1])

```

### Gather person data

```{r}
more_info <- fromJSON(person_link)
# more_info <- fromJSON(person_link_example1)

# more_info
```


Now, `more_info` is our list.  We can use code exmaples from "more-futzing.Rmd" to figure out how to gather data from an indivual  (See section:  Building a Custom Data Frame)


### Create Big Data Frame 

```{r}
Big_data_frame <- tibble(
  name = more_info$label,
  title = more_info$title,
  #awards = as.list(sad_person$awards$label)
  #awards = map(sad_person$awards$label, 1)
  NetID = more_info$attributes$netid
)

# tibble is similar to as.data.frame

#person_awards_df$awards[3]
Big_data_frame
```

###  Add Next person

```{r}
foo_person_uri <- "https://scholars.duke.edu/individual/per5862252"

person_link <- glue(baseurl, foo_person_uri)
```


```{r}
more_info <- fromJSON(person_link)
# more_info
```

### Add Rows to Data Frame


```{r}
Big_data_frame <- add_row(Big_data_frame,
                          name = more_info$label,
                          title = more_info$title,
                          NetID = more_info$attributes$netid)

Big_data_frame
```

### Add Next Person

```{r}
baseurl <- "https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri="

person_link <- glue(baseurl, org_links$uri[2])

```

```{r}
more_info <- fromJSON(person_link)
# more_info <- fromJSON(person_link_example1)
```

### Add Rows to Data Frame

```{r}
Big_data_frame <- add_row(Big_data_frame,
                          name = more_info$label,
                          title = more_info$title,
                          NetID = more_info$attributes$netid)

Big_data_frame
```



