---
title: "Testing our Idea"
output: html_notebook
---

## Load Packages

```{r}
library(jsonlite)
library(tidyverse)
```

## Get Scholars @ Directory information


```{r}
org_rec <- "https://scholars.duke.edu/widgets/api/v0.9/organizations/people/all.json?uri=https://scholars.duke.edu/individual/org50000498&formatting=detailed&style=yes&start=&end="
```


```{r}
(org_links <- fromJSON(URLencode(org_rec)))
```


## Logic Outline

Using either a for loop or map, loop over each row of the org_links data frame, take the uri field and gather more information.

more_info <- org_links$uri

### Example

build a URL:

https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri=org_links$uri[1]


```{r}
baseurl <- "https://scholars.duke.edu/widgets/api/v0.9/people/complete/all.json?uri="

foo_person_uri <- "https://scholars.duke.edu/individual/per5862252"

person_link_example1 <- glue::glue(baseurl, org_links$uri[1])

person_link <- glue::glue(baseurl, foo_person_uri)

```


```{r}
more_info <- fromJSON(person_link)
#more_info <- fromJSON(person_link_example1)

more_info
```


Now, `more_info` is our list.  We can use code exmaples from "more-futzing.Rmd" to figure out how to gather data from an indivual  (See section:  Building a Custom Data Frame)


